A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.

### 2022-04-13 inst/manuscript/supporting.tex
section 2 and supporting updates

\usepackage{lineno} % add
  \linenumbers % turns line numbering on
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A comparison of design-based and model-based approaches for finite population spatial data -- Supporting Information.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
\begin{frontmatter}

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supporting Information.}
    \author[USEPA]{Michael Dumelle\corref{1}}

@@

\hypertarget{sec:simtabs}{%
\section{Simulation Study Tables}\label{sec:simtabs}}

Recall the four sampling-analysis combinations from the simulation
study, summarized in Table \ref{tab:designanalysis}. Also recall the 36
parameter configurations from the simulation study, summarized in Table
\ref{tab:parmtab}.

\begin{table}[ht]
\centering
\begin{tabular}{r|ll}
  \hline
 & Design & Model \\ 
  \hline
IRS & IRS-Design & IRS-Model \\ 
  GRTS & GRTS-Design & GRTS-Model \\ 
   \hline
\end{tabular}
\caption{\label{tab:designanalysis} Sampling-analysis combinations in the simulation study. The rows give the two types of sampling designs and the columns give the two types of analyses.} 
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{r|lll}
   \hline
Sample Size (n) & 50 & 100 & 200 \\ 
  Layout & Random & Gridded & - \\ 
  Proportion of Dependent Error & 0 & 0.5 & 0.9 \\ 
  Response Type & Normal & Lognormal & - \\ 
   \hline
\end{tabular}
\caption{\label{tab:parmtab} Simulation scenario options. All combinations of sample size, location layout, response type, and proportion of dependent random error composed the 36 simulation scenarios. In each simualtion scenario, the total variance was 2.} 
\end{table}

Next we present tables summarizing mean estimation bias (design-based)
or mean prediction bias (model-based), root-mean-squared error
(design-based) or root-mean-squared-prediction error (model-based), and
95\% confidence interval coverage (design-based) or 95\% prediction
interval coverage (model-based) for all 36 simulation scenarios.

@@

\scalebox{0.85}{

@@

Approach & Layout & Response & DE Prop & n & Bias & rMS(P)E & Coverage \\ 

@@

IRS-Design & Gridded & Normal & 0 & 50 & -0.0023 & 0.1968 & 0.9440 \\ 
  IRS-Model & Gridded & Normal & 0 & 50 & -0.0029 & 0.1988 & 0.9400 \\ 
  GRTS-Design & Gridded & Normal & 0 & 50 & -0.0011 & 0.1946 & 0.9110 \\ 
  GRTS-Model & Gridded & Normal & 0 & 50 & -0.0006 & 0.1949 & 0.9300 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 50 & -0.0036 & 0.2007 & 0.9080 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 50 & -0.0094 & 0.2071 & 0.9045 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 50 & -0.0007 & 0.1962 & 0.8690 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 50 & -0.0022 & 0.1969 & 0.8945 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

IRS-Design & Random & Normal & 0 & 50 & 0.0019 & 0.1861 & 0.9505 \\ 
  IRS-Model & Random & Normal & 0 & 50 & 0.0014 & 0.1892 & 0.9445 \\ 
  GRTS-Design & Random & Normal & 0 & 50 & -0.0040 & 0.1955 & 0.9090 \\ 
  GRTS-Model & Random & Normal & 0 & 50 & -0.0040 & 0.1965 & 0.9315 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

IRS-Design & Random & Lognormal & 0 & 50 & 0.0032 & 0.1843 & 0.9205 \\ 
  IRS-Model & Random & Lognormal & 0 & 50 & -0.0039 & 0.1945 & 0.9105 \\ 
  GRTS-Design & Random & Lognormal & 0 & 50 & -0.0056 & 0.1944 & 0.8870 \\ 
  GRTS-Model & Random & Lognormal & 0 & 50 & -0.0078 & 0.1967 & 0.9075 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 50 & 0.0025 & 0.1762 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 50 & 0.0007 & 0.1655 & 0.9305 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 50 & 0.0004 & 0.1524 & 0.9115 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 50 & -0.0003 & 0.1499 & 0.9320 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0004 & 0.1863 & 0.9140 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0076 & 0.1834 & 0.9035 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 50 & 0.0016 & 0.1612 & 0.8810 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 50 & -0.0017 & 0.1606 & 0.8940 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

IRS-Design & Random & Normal & 0.5 & 50 & 0.0037 & 0.1657 & 0.9590 \\ 
  IRS-Model & Random & Normal & 0.5 & 50 & 0.0027 & 0.1546 & 0.9495 \\ 
  GRTS-Design & Random & Normal & 0.5 & 50 & -0.0034 & 0.1511 & 0.9170 \\ 
  GRTS-Model & Random & Normal & 0.5 & 50 & -0.0037 & 0.1504 & 0.9305 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

IRS-Design & Random & Lognormal & 0.5 & 50 & 0.0023 & 0.1637 & 0.9245 \\ 
  IRS-Model & Random & Lognormal & 0.5 & 50 & -0.0055 & 0.1622 & 0.9125 \\ 
  GRTS-Design & Random & Lognormal & 0.5 & 50 & -0.0057 & 0.1570 & 0.9000 \\ 
  GRTS-Model & Random & Lognormal & 0.5 & 50 & -0.0079 & 0.1567 & 0.9100 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

IRS-Design & Gridded & Normal & 0.9 & 50 & 0.0053 & 0.1579 & 0.9470 \\ 
  IRS-Model & Gridded & Normal & 0.9 & 50 & 0.0026 & 0.1165 & 0.9315 \\ 
  GRTS-Design & Gridded & Normal & 0.9 & 50 & 0.0013 & 0.1074 & 0.9220 \\ 
  GRTS-Model & Gridded & Normal & 0.9 & 50 & -0.0007 & 0.0949 & 0.9430 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

IRS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1731 & 0.9220 \\ 
  IRS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0020 & 0.1325 & 0.9135 \\ 
  GRTS-Design & Gridded & Lognormal & 0.9 & 50 & 0.0031 & 0.1183 & 0.9065 \\ 
  GRTS-Model & Gridded & Lognormal & 0.9 & 50 & -0.0002 & 0.1090 & 0.9120 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

IRS-Design & Random & Normal & 0.9 & 50 & 0.0062 & 0.1520 & 0.9525 \\ 
  IRS-Model & Random & Normal & 0.9 & 50 & 0.0037 & 0.1074 & 0.9525 \\ 
  GRTS-Design & Random & Normal & 0.9 & 50 & -0.0029 & 0.1038 & 0.9340 \\ 
  GRTS-Model & Random & Normal & 0.9 & 50 & -0.0027 & 0.0940 & 0.9360 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

IRS-Design & Random & Lognormal & 0.9 & 50 & 0.0053 & 0.1542 & 0.9325 \\ 
  IRS-Model & Random & Lognormal & 0.9 & 50 & -0.0012 & 0.1160 & 0.9115 \\ 
  GRTS-Design & Random & Lognormal & 0.9 & 50 & -0.0033 & 0.1150 & 0.9160 \\ 
  GRTS-Model & Random & Lognormal & 0.9 & 50 & -0.0031 & 0.1014 & 0.9235 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

IRS-Design & Gridded & Normal & 0 & 100 & -0.0029 & 0.1322 & 0.9430 \\ 
  IRS-Model & Gridded & Normal & 0 & 100 & -0.0033 & 0.1332 & 0.9410 \\ 
  GRTS-Design & Gridded & Normal & 0 & 100 & 0.0041 & 0.1302 & 0.9245 \\ 
  GRTS-Model & Gridded & Normal & 0 & 100 & 0.0038 & 0.1304 & 0.9420 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

IRS-Design & Gridded & Lognormal & 0 & 100 & -0.0052 & 0.1334 & 0.9335 \\ 
  IRS-Model & Gridded & Lognormal & 0 & 100 & -0.0072 & 0.1350 & 0.9300 \\ 
  GRTS-Design & Gridded & Lognormal & 0 & 100 & 0.0042 & 0.1303 & 0.9035 \\ 
  GRTS-Model & Gridded & Lognormal & 0 & 100 & 0.0034 & 0.1307 & 0.9265 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

IRS-Design & Random & Normal & 0 & 100 & -0.0066 & 0.1366 & 0.9405 \\ 
  IRS-Model & Random & Normal & 0 & 100 & -0.0067 & 0.1370 & 0.9385 \\ 
  GRTS-Design & Random & Normal & 0 & 100 & 0.0028 & 0.1364 & 0.9180 \\ 
  GRTS-Model & Random & Normal & 0 & 100 & 0.0029 & 0.1363 & 0.9345 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

IRS-Design & Random & Lognormal & 0 & 100 & -0.0051 & 0.1348 & 0.9280 \\ 
  IRS-Model & Random & Lognormal & 0 & 100 & -0.0075 & 0.1372 & 0.9230 \\ 
  GRTS-Design & Random & Lognormal & 0 & 100 & 0.0002 & 0.1375 & 0.8840 \\ 
  GRTS-Model & Random & Lognormal & 0 & 100 & -0.0003 & 0.1377 & 0.9090 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

IRS-Design & Gridded & Normal & 0.5 & 100 & -0.0016 & 0.1177 & 0.9540 \\ 
  IRS-Model & Gridded & Normal & 0.5 & 100 & -0.0023 & 0.1072 & 0.9470 \\ 
  GRTS-Design & Gridded & Normal & 0.5 & 100 & 0.0051 & 0.0998 & 0.9300 \\ 
  GRTS-Model & Gridded & Normal & 0.5 & 100 & 0.0039 & 0.0982 & 0.9470 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

IRS-Design & Gridded & Lognormal & 0.5 & 100 & -0.0021 & 0.1211 & 0.9445 \\ 
  IRS-Model & Gridded & Lognormal & 0.5 & 100 & -0.0058 & 0.1153 & 0.9295 \\ 
  GRTS-Design & Gridded & Lognormal & 0.5 & 100 & 0.0041 & 0.1090 & 0.9085 \\ 
  GRTS-Model & Gridded & Lognormal & 0.5 & 100 & 0.0019 & 0.1090 & 0.9180 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

IRS-Design & Random & Normal & 0.5 & 100 & -0.0064 & 0.1222 & 0.9440 \\ 
  IRS-Model & Random & Normal & 0.5 & 100 & -0.0049 & 0.1073 & 0.9440 \\ 
  GRTS-Design & Random & Normal & 0.5 & 100 & 0.0013 & 0.1041 & 0.9155 \\ 
  GRTS-Model & Random & Normal & 0.5 & 100 & 0.0014 & 0.1020 & 0.9400 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DE Prop), sample size (n), mean (prediction) bias (Bias), root-mean-squared-(prediction) error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 19.} 

>>>>

\usepackage{lineno} % add
  \linenumbers % turns line numbering on

\usepackage{graphicx}
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\bibliographystyle{elsarticle-harv}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={A comparison of design-based and model-based approaches for finite population spatial data -- Supporting information.},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}

\begin{frontmatter}

  \title{A comparison of design-based and model-based approaches for finite
population spatial data -- Supporting information.}
    \author[USEPA]{Michael Dumelle\corref{1}}

@@

Recall the four sampling-analysis combinations from the simulated and
real data: simple random sampling with design-based inference (SRS-DB),
simple random sapling with model-based inference (SRS-MB), GRTS sampling
with design-based inference (GRTS-DB), and GRTS sampling with
model-based inference (GRTS-MB).

\hypertarget{sec:simtabs}{%
\section{Simulated Data}\label{sec:simtabs}}

For the simulated data, we considered 36 parameter configurations -- the
crossing of three sample sizes (\(n = 50\), \(n = 100\), \(n = 200)\),
two location layouts (random and gridded), three proportions of
dependent random error (DRE) (0\%, 50\%, 90\%), and two response types
(normal and skewed).

Next we present tables summarizing mean bias, RMSE, and interval
coverage for all 36 simulation scenarios.

@@

\scalebox{0.8}{

@@

Approach & Layout & Response & DRE\% & n & MB & RMSE & Coverage \\ 

@@

SRS-DB & Gridded & Normal & 0\% & 50 & 0.0004 & 0.1922 & 0.9345 \\ 
  SRS-MB & Gridded & Normal & 0\% & 50 & -0.0112 & 0.1930 & 0.9420 \\ 
  GRTS-DB & Gridded & Normal & 0\% & 50 & 0.0005 & 0.1914 & 0.9170 \\ 
  GRTS-MB & Gridded & Normal & 0\% & 50 & -0.0112 & 0.1905 & 0.9490 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 1.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 50 & 0.0004 & 0.1965 & 0.8955 \\ 
  SRS-MB & Gridded & Skewed & 0\% & 50 & -0.0110 & 0.2055 & 0.9045 \\ 
  GRTS-DB & Gridded & Skewed & 0\% & 50 & 0.0025 & 0.1947 & 0.8710 \\ 
  GRTS-MB & Gridded & Skewed & 0\% & 50 & -0.0048 & 0.1988 & 0.9110 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 2.} 

@@

SRS-DB & Random & Normal & 0\% & 50 & -0.0002 & 0.1964 & 0.9295 \\ 
  SRS-MB & Random & Normal & 0\% & 50 & 0.0045 & 0.1953 & 0.9395 \\ 
  GRTS-DB & Random & Normal & 0\% & 50 & -0.0004 & 0.1951 & 0.9065 \\ 
  GRTS-MB & Random & Normal & 0\% & 50 & 0.0031 & 0.1940 & 0.9425 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 3.} 

@@

SRS-DB & Random & Skewed & 0\% & 50 & 0.0016 & 0.1941 & 0.8985 \\ 
  SRS-MB & Random & Skewed & 0\% & 50 & -0.0059 & 0.1932 & 0.9130 \\ 
  GRTS-DB & Random & Skewed & 0\% & 50 & 0.0041 & 0.1910 & 0.8740 \\ 
  GRTS-MB & Random & Skewed & 0\% & 50 & 0.0000 & 0.1861 & 0.9225 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 4.} 

@@

SRS-DB & Gridded & Normal & 50\% & 50 & -0.0031 & 0.1472 & 0.9400 \\ 
  SRS-MB & Gridded & Normal & 50\% & 50 & -0.0007 & 0.1617 & 0.9355 \\ 
  GRTS-DB & Gridded & Normal & 50\% & 50 & -0.0030 & 0.1501 & 0.9205 \\ 
  GRTS-MB & Gridded & Normal & 50\% & 50 & -0.0013 & 0.1775 & 0.9460 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 5.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 50 & -0.0060 & 0.1605 & 0.9085 \\ 
  SRS-MB & Gridded & Skewed & 50\% & 50 & -0.0083 & 0.1787 & 0.8990 \\ 
  GRTS-DB & Gridded & Skewed & 50\% & 50 & -0.0041 & 0.1610 & 0.8995 \\ 
  GRTS-MB & Gridded & Skewed & 50\% & 50 & -0.0047 & 0.1891 & 0.9100 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 6.} 

@@

SRS-DB & Random & Normal & 50\% & 50 & -0.0097 & 0.1507 & 0.9315 \\ 
  SRS-MB & Random & Normal & 50\% & 50 & 0.0042 & 0.1615 & 0.9350 \\ 
  GRTS-DB & Random & Normal & 50\% & 50 & -0.0092 & 0.1513 & 0.9165 \\ 
  GRTS-MB & Random & Normal & 50\% & 50 & 0.0061 & 0.1744 & 0.9445 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 7.} 

@@

SRS-DB & Random & Skewed & 50\% & 50 & -0.0021 & 0.1624 & 0.9000 \\ 
  SRS-MB & Random & Skewed & 50\% & 50 & -0.0051 & 0.1808 & 0.9065 \\ 
  GRTS-DB & Random & Skewed & 50\% & 50 & 0.0021 & 0.1618 & 0.8880 \\ 
  GRTS-MB & Random & Skewed & 50\% & 50 & 0.0014 & 0.1804 & 0.9195 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 8.} 

@@

SRS-DB & Gridded & Normal & 90\% & 50 & -0.0037 & 0.0960 & 0.9400 \\ 
  SRS-MB & Gridded & Normal & 90\% & 50 & 0.0044 & 0.1137 & 0.9435 \\ 
  GRTS-DB & Gridded & Normal & 90\% & 50 & -0.0021 & 0.1072 & 0.9280 \\ 
  GRTS-MB & Gridded & Normal & 90\% & 50 & 0.0055 & 0.1621 & 0.9355 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 9.} 

@@

SRS-DB & Gridded & Skewed & 90\% & 50 & -0.0039 & 0.1039 & 0.9205 \\ 
  SRS-MB & Gridded & Skewed & 90\% & 50 & -0.0011 & 0.1217 & 0.9130 \\ 
  GRTS-DB & Gridded & Skewed & 90\% & 50 & -0.0017 & 0.1129 & 0.9180 \\ 
  GRTS-MB & Gridded & Skewed & 90\% & 50 & 0.0007 & 0.1546 & 0.9345 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 10.} 

@@

SRS-DB & Random & Normal & 90\% & 50 & -0.0011 & 0.0940 & 0.9410 \\ 
  SRS-MB & Random & Normal & 90\% & 50 & 0.0045 & 0.1093 & 0.9445 \\ 
  GRTS-DB & Random & Normal & 90\% & 50 & -0.0017 & 0.1054 & 0.9295 \\ 
  GRTS-MB & Random & Normal & 90\% & 50 & 0.0058 & 0.1575 & 0.9470 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 11.} 

@@

SRS-DB & Random & Skewed & 90\% & 50 & -0.0026 & 0.1127 & 0.9225 \\ 
  SRS-MB & Random & Skewed & 90\% & 50 & -0.0046 & 0.1301 & 0.9180 \\ 
  GRTS-DB & Random & Skewed & 90\% & 50 & -0.0026 & 0.1250 & 0.9175 \\ 
  GRTS-MB & Random & Skewed & 90\% & 50 & -0.0022 & 0.1772 & 0.9305 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 12.} 

@@

SRS-DB & Gridded & Normal & 0\% & 100 & -0.0010 & 0.1352 & 0.9445 \\ 
  SRS-MB & Gridded & Normal & 0\% & 100 & -0.0026 & 0.1362 & 0.9405 \\ 
  GRTS-DB & Gridded & Normal & 0\% & 100 & -0.0011 & 0.1345 & 0.9210 \\ 
  GRTS-MB & Gridded & Normal & 0\% & 100 & -0.0028 & 0.1352 & 0.9475 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 13.} 

@@

SRS-DB & Gridded & Skewed & 0\% & 100 & 0.0077 & 0.1307 & 0.9155 \\ 
  SRS-MB & Gridded & Skewed & 0\% & 100 & -0.0024 & 0.1412 & 0.9150 \\ 
  GRTS-DB & Gridded & Skewed & 0\% & 100 & 0.0082 & 0.1304 & 0.8945 \\ 
  GRTS-MB & Gridded & Skewed & 0\% & 100 & -0.0001 & 0.1384 & 0.9210 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 14.} 

@@

SRS-DB & Random & Normal & 0\% & 100 & 0.0019 & 0.1318 & 0.9460 \\ 
  SRS-MB & Random & Normal & 0\% & 100 & -0.0007 & 0.1344 & 0.9435 \\ 
  GRTS-DB & Random & Normal & 0\% & 100 & 0.0021 & 0.1315 & 0.9280 \\ 
  GRTS-MB & Random & Normal & 0\% & 100 & -0.0004 & 0.1339 & 0.9450 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 15.} 

@@

SRS-DB & Random & Skewed & 0\% & 100 & 0.0039 & 0.1315 & 0.9230 \\ 
  SRS-MB & Random & Skewed & 0\% & 100 & 0.0005 & 0.1342 & 0.9280 \\ 
  GRTS-DB & Random & Skewed & 0\% & 100 & 0.0043 & 0.1311 & 0.8990 \\ 
  GRTS-MB & Random & Skewed & 0\% & 100 & 0.0021 & 0.1322 & 0.9280 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 16.} 

@@

SRS-DB & Gridded & Normal & 50\% & 100 & -0.0003 & 0.0993 & 0.9435 \\ 
  SRS-MB & Gridded & Normal & 50\% & 100 & -0.0007 & 0.1058 & 0.9425 \\ 
  GRTS-DB & Gridded & Normal & 50\% & 100 & 0.0000 & 0.1003 & 0.9300 \\ 
  GRTS-MB & Gridded & Normal & 50\% & 100 & -0.0025 & 0.1207 & 0.9420 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 17.} 

@@

SRS-DB & Gridded & Skewed & 50\% & 100 & -0.0019 & 0.1127 & 0.9175 \\ 
  SRS-MB & Gridded & Skewed & 50\% & 100 & 0.0002 & 0.1135 & 0.9160 \\ 
  GRTS-DB & Gridded & Skewed & 50\% & 100 & 0.0000 & 0.1113 & 0.9025 \\ 
  GRTS-MB & Gridded & Skewed & 50\% & 100 & 0.0023 & 0.1221 & 0.9315 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 18.} 

@@

SRS-DB & Random & Normal & 50\% & 100 & -0.0010 & 0.0997 & 0.9380 \\ 
  SRS-MB & Random & Normal & 50\% & 100 & -0.0001 & 0.1079 & 0.9440 \\ 
  GRTS-DB & Random & Normal & 50\% & 100 & -0.0012 & 0.1012 & 0.9235 \\ 
  GRTS-MB & Random & Normal & 50\% & 100 & -0.0016 & 0.1214 & 0.9440 \\ 

@@

\caption{Sampling-analysis combination (Approach), population layout (Layout), response type (Response), proportion of dependent random error (DRE\%), sample size (n), mean bias (MB), root-mean-squared error (rMS(P)E), and 95\% interval coverage (Coverage) in simulation scenario 19.} 
